### 2013-04-16 projects/term_paper/paper.tex

\title{CIS 343: Programming Language Survey Paper on Haskell}
\author{
        Kurt O'Hearn\\
        Nicholas Olesak\\
}
\date{\today}

\documentclass[12pt]{article}

\begin{document}
\maketitle

\section{Introduction}
[TODO]~\cite{learnyouahaskell}

\section{Data and Control Abstractions}

\subsection{Data Types and Type Checking}
\subsection{Control Flow Mechanisms}

\section{Advanced Topics}

\subsection{Inheritance}
\subsection{Concurrency Support}
\subsection{Introspection}

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}

### 2013-04-17 projects/term_paper/paper.tex
Added exemplary code using the minted packaged to typeset Haskell code.
Added paper outline and began adding source code examples.

@@
-\title{CIS 343: Programming Language Survey Paper on Haskell}
+% Author: Kurt O'Hearn
+% Author: Nicholas Olesak
+% Date: April 15, 2013
+% Class: CIS 343-02
+% Purpose: Progamming Language Survey Term Paper on Haskell
+\documentclass[titlepage,12pt]{article}
+
+\usepackage{minted}
+
+% aliases
+\newcommand{\be}{\begin{enumerate}}
+\newcommand{\bi}{\begin{itemize}}
+\newcommand{\ee}{\end{enumerate}}
+\newcommand{\ei}{\end{itemize}}
+
+\title{Programming Language Survey Paper on Haskell}
 \author{
@@
 
-\documentclass[12pt]{article}
+\begin{document}
 
-\begin{document}
 \maketitle 
+\setcounter{tocdepth}{3}
+\tableofcontents \newpage
 
 \section{Introduction}
+\bi
+    \item Origin and history
+    \item Explanation of the functional programming paradigm
+    \item Application domains of the language
+\ei
 [TODO]~\cite{learnyouahaskell}
+\begin{minted}{haskell}
+module Main where
+import Data.List
+
+main :: IO ()
+main = putStrLn "Hello World!" >> test
+
+test = do 
+    print 123
+\end{minted}
 
@@
 
-\subsection{Data Types and Type Checking}
-\subsection{Control Flow Mechanisms}
+\subsection{Data Abstractions}
+\subsubsection{Data Types}
+\bi
+    \item Basis data types: Int, Float, Char, Boolean, lists
+\begin{minted}{haskell}
+let i = 2
+let x = 3.14
+let c = 'c'
+let str = ['H','a','s','k','e','l','l','!']
+; shorthand for the above
+let str2 = "Haskell!"
+\end{minted}
+
+    \item Type variables: variables that can be any type (used in polymorphic functions)
+\begin{minted}{haskell}
+lastTwo :: [a] -> [a]
+lastTwo a = [a !! ((length a) - 2), a !! ((length a) - 1)]
+\end{minted}
+\ei
+
+\subsubsection{Type Checking}
+\bi
+    \item Haskell: static typing, type inferencing by context
+\begin{minted}{haskell}
+let myStr = "2"
+; will result in an exception as the desired type to convert to is
+; ambiguous since Haskell has no context to infer the type
+let myNum = read myStr
+; not ambiguous, as the compiler infers the Int type is desired
+let myNum2 = (read myStr) + 2
+\end{minted}
+    \item Type classes: Eq, Ord, Show/Read, Bounded, Enum, Num/Integral/Floating
+\ei
+
+\subsection{Control Abstractions}
+\subsubsection{Expressions}
+\bi
+    \item Function definitions
+    \item Binding: let, where
+\ei
+
+\subsubsection{Operators and Precedence}
+\bi
+    \item Operators: postfix notation, naming typically consists of symbols
+    \item Functions: infix notation, named using alphanumeric characters in camel case
+    \item Any function can be used as an operator by calling it in postfix notation
+\begin{minted}{haskell}
+f (Int a) => a -> a
+f a b = a + b
+; invoke the function in postfix notation
+print (1 `f` 2)
+\end{minted}
+    \item Any operator can be called as a function in infix notation
+\begin{minted}{haskell}
+print ((+) 2 5)
+\end{minted}
+    \item Operators can be overloaded
+\begin{minted}{haskell}
+* a b = a * a * b
+print (2 * 3)
+\end{minted}
+\ei
+
+\subsubsection{Selection Constructs}
+\bi
+    \item Pattern matching
+    \item if/then/else
+    \item Guards
+    \item Case expression
+\ei
+
+\subsubsection{Iterative Constructs}
+\bi
+    \item List comprehensions
+    \item Map/fold
+    \item Recursion
+\ei
+
+\subsubsection{Functions}
+\bi
+    \item Definition/use
+    \item Support parameter passing techniques
+\ei
+
+\subsubsection{Scoping}
+\bi
+    \item Static
+\ei
+
+\subsubsection{Modules}
+
+\subsubsection{Exception Handling}
 

### 2013-04-17 projects/term_paper/paper.tex
Fixed a few errors in the code.
Continued adding code samples.

@@
 \begin{minted}{haskell}
-f (Int a) => a -> a
+f :: (Int a) => a -> a -> a
 f a b = a + b
@@
 \begin{minted}{haskell}
-* a b = a * a * b
+(*) :: (Num a) => a -> a -> a
+(*) a b = a * a * b
 print (2 * 3)
@@
     \item Pattern matching
+\begin{minted}{haskell}
+favoriteLang :: String -> String
+favoriteLang "Haskell" = "You have refined taste, my friend."
+favoriteLang "Clojure" = 
+    "The wise do not build a house on unsturdy ground."
+favoriteLang lang = lang ++ 
+    " is a fine choice, but you should give Haskell a spin."
+\end{minted}
     \item if/then/else
     \item Guards
+\begin{minted}{haskell}
+let balance = 200
+assessWorth :: Int -> String
+assessWorth =
+    | balance >= 100000 = "You're rich!"
+    | balance >= 100 = "You're rich by student standards!"
+    | otherwise = "Need a loan, friend?"
+\end{minted}
     \item Case expression

### 2013-04-17 projects/term_paper/paper.tex
Merged in Nick's introduction and added more code examples.

@@
 \section{Introduction}
-\bi
-    \item Origin and history
-    \item Explanation of the functional programming paradigm
-    \item Application domains of the language
-\ei
+This paper provides an overview of the Haskell programming language.
+
+\subsection{Origin and History}
+
+In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description and evaluation of functions in mathematics (Haskell).
+Lambda calculus became the foundation for functional programming (``Haskell'').
+However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there became the need for a standard functional language to aid the spread of functional programming (Hudak 1).
+A meeting was held in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need (Hudak 1).
+The meeting resulted in the formation of a committee to design a standard functional language.
+In 1990, the committee produced their result: a consolidation of existing functional programming languages into an open standard, common language to be used for functional programming research: Haskell (Hudak 3).
+
+Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming.
+It has a lambda as its logo to symbolize lambda calculus as its foundation.
+Today, Haskell is widely used in many different aspects of computing.
+From AT\&T's automated processing of abuse complaints in its network security division to the National Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of modern industry (``Haskell'').
+
+\subsection{Functional Programming Paradigm}
+
+Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values.
+Each functions acts independently of other functions, and does not change the state of anything outside of its scope.
+This is referred to as having no ``side-effects,'' and it allows Haskell to be exceptionally optimized and permit parallel processing.
+In addition, functions do not have to be declared in a particular order since they all exist independently of one another.
+
+In addition, it is also a lazy language; expressions in Haskell are not evaluated at binding time, but rather are evaluated only when the result is needed.
+
+Type checking in Haskell is static and is performed at compile time.
+Haskell uses type-declarations for functions, in which the types of parameters and return values are explicitly defined.
+Any use of a function in which parameters do not meet the defined function type is flagged by the compiler, and compilation will be aborted.
+For example, the following function defines
+
+\subsection{Application Domains}
+
 [TODO]~\cite{learnyouahaskell}
@@
 \bi
-    \item Basis data types: Int, Float, Char, Boolean, lists
+    \item Basis data types: Int, Float, Char, Boolean, lists, tuples
 \begin{minted}{haskell}
@@
 let str2 = "Haskell!"
+let t = (3.14, 'pi')
 \end{minted}
@@
     \item Function definitions
-    \item Binding: let, where
+\begin{minted}{haskell}
+greet :: String -> String
+greet name = "Hello, " ++ name ++ "!"
+\end{minted}
+    \item Bindings: let/in (valid expression), where (locally bound to a syntactic construct)
+\begin{minted}{haskell}
+rectPrismVol :: (Num a) -> a -> a -> a -> a
+rectPrismVol length width height = 4 * (faceArea length width)
+    + 2 * (baseArea length height)
+where   faceArea l w = l * w
+        baseArea = l * h
+\end{minted}
+\begin{minted}{haskell}
+myExp =
+    let e = 2.7182
+    in  e ** x
+\end{minted}
+NOTE: statements in let/in must be aligned in same column
 \ei
@@
     \item if/then/else
+\begin{minted}{haskell}
+guessGame :: Int -> String
+guessGame x = if x == 42
+    then "You have a deep understanding of life."
+    else "You need to think more about life."
+\end{minted}
     \item Guards
@@
     \item Case expression
+\begin{minted}{haskell}
+favoriteMathSymbol :: String -> String
+favoriteMathSymbol x = case x of
+    "Pi" -> "Geometry is your mind's eye."
+    "e" -> "May the calculus forever be with you."
+    "Epsilon" -> "I think I am within the limit, "
+        ++ "therefore, I am within the limit."
+    x = "You have much to learn of the maths."
+\end{minted}
 \ei
@@
     \item List comprehensions
+\begin{minted}{haskell}
+filterModThree :: [Int] -> [Int]
+filterModThree xs = [x | x <- xs, x `mod` 3 == 0]
+\end{minted}
     \item Map/fold
@@
     \item Definition/use
-    \item Support parameter passing techniques
+    \item Parameter passing techniques
 \ei

### 2013-04-20 projects/term_paper/paper.tex
More work on paper

@@
 \subsubsection{Data Types}
-\bi
-    \item Basis data types: Int, Float, Char, Boolean, lists, tuples
+
+Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values.
+Sub-data types for numbers exist to explicitly define characteristics of the type of number represented.
+For example, Haskell has two types of integers: Int and Integer.
+Int has the system-defined maximum integer size as its range while Integer’s ranged is only bound by the available amount of memory, and thus re used for arbitrary precision integers.
+Haskell also has two floating point types: Float and Double, where a Double has twice the floating point precision of a Float.
+
+Two more essential data types in Haskell are lists and tuples.
+Lists are the most used data type due to their expendability and the wide range of functions that are available to manipulate them.
+They can easily be created, traversed, concatenated, reversed, sorted, and more with standard, built-in functions.
+Lists, however, are homogeneous and can only contain elements of the same data type.
+Tuples, on the other hand, can be heterogeneous.
+They are useful when the types and exact number of values to be combined are known.
+Like lists, tuples also comes with a surplus of built-in functions, one of which is the ability to zip two lists into one by joining matching elements into pairs.
+Simple yet elegant code can be written which combines the attributes of lists, tuples, and the other various other data types in Haskell.
+
 \begin{minted}{haskell}

### 2013-04-20 projects/term_paper/paper.tex
update

@@
 \subsubsection{Data Types}
-
 Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values.
@@
 Simple yet elegant code can be written which combines the attributes of lists, tuples, and the other various other data types in Haskell.
+
+Haskell also has a String data type.
+Although Strings are represented by double quotations, they are actually stored as a list of characters.
+Thus, when specificying a data type, String and [Char] are equivalent.
 

### 2013-04-21 projects/term_paper/paper.tex
more work on paper

@@
 
-Type checking in Haskell is static and is performed at compile time.
-Haskell uses type-declarations for functions, in which the types of parameters and return values are explicitly defined.
-Any use of a function in which parameters do not meet the defined function type is flagged by the compiler, and compilation will be aborted.
-For example, the following function defines
-
 \subsection{Application Domains}
@@
 
+\begin{minted}{haskell}
+let x = 2
+let pi = 3.14
+let c = 'c'
+\end{minted}
+
 Two more essential data types in Haskell are lists and tuples.
@@
 
+\begin{minted}{haskell}
+let evens = [2, 4, 6, 8, 10]	-- list
+let t = (3.14, 'pi')		-- tuple
+\end{minted}
+
 Haskell also has a String data type.
 Although Strings are represented by double quotations, they are actually stored as a list of characters.
-Thus, when specificying a data type, String and [Char] are equivalent.
+Thus, when specifiying a data type, String is equivalent to [Char].
 
 \begin{minted}{haskell}
-let i = 2
-let x = 3.14
-let c = 'c'
-let str = ['H','a','s','k','e','l','l','!']
-; shorthand for the above
-let str2 = "Haskell!"
-let t = (3.14, 'pi')
+let str1 = ['H','a','s','k','e','l','l','!']
+let str2 = "Haskell!" 	-- a string representation of str1
 \end{minted}
 
-    \item Type variables: variables that can be any type (used in polymorphic functions)
+In addition to these basic data types, Haskell also offers type variables.
+Type variables are variables whose type has not been explicitly declared; rather, they can be any type.
+By defining a function without declaring data types, the variables in the function can be used as any type and the function can be polymorphic.
+In the following example, the function can handle a list of any type because its uses a type variable.
+
 \begin{minted}{haskell}
@@
 \end{minted}
-\ei
 
 \subsubsection{Type Checking}
-\bi
-    \item Haskell: static typing, type inferencing by context
+Type checking in Haskell is performed statically at compile time.
+Haskell uses type-declarations for functions, in which the types of parameters and return values are explicitly defined.
+Any use of a function in which parameters do not meet the defined function type is flagged by the compiler, and compilation will be aborted.
+In addition, ues type inferencing by context.
+The type system in Haskell deduces obvious types and makes them concrete.
+In the following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type is desired because myNum is added to an Int.
+
 \begin{minted}{haskell}
 let myStr = "2" 
-; will result in an exception as the desired type to convert to is
-; ambiguous since Haskell has no context to infer the type
-let myNum = read myStr
-; not ambiguous, as the compiler infers the Int type is desired
 let myNum2 = (read myStr) + 2
 \end{minted}
-    \item Type classes: Eq, Ord, Show/Read, Bounded, Enum, Num/Integral/Floating
-\ei
+
+If the context does not suggest the type, as in the example below, then an exception will result.
+
+\begin{minted}{haskell}
+let myStr = "2" 
+let myNum = read myStr
+\end{minted}
+
+Haskell uses typeclasses to categorize the type system.
+Typeclasses define the behavior of a general type.
+A type must support the definition of its typeclass, but may also be more specific.
+For example, all of the operators in Haskell are categorized under the Eq typeclass.
+Other examples of typeclasses in Haskell include Ord, Show, Read, Enum, Num, Integral, and Floating.
+Typeclasses can be used to allow multiple types to be passed to a function.
+For example, to create a function that will accept both Int and Integer types, it's as simple as declaring its typeclass as Integral.
 

### 2013-04-21 projects/term_paper/paper.tex
More updates. Got LaTeX Full working

@@
 Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values.
-Each functions acts independently of other functions, and does not change the state of anything outside of its scope.
-This is referred to as having no ``side-effects,'' and it allows Haskell to be exceptionally optimized and permit parallel processing.
+Every function acts independently of other functions and does not change the state of anything outside of its scope.
+This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as well as to permit parallel processing.
 In addition, functions do not have to be declared in a particular order since they all exist independently of one another.
-
-In addition, it is also a lazy language; expressions in Haskell are not evaluated at binding time, but rather are evaluated only when the result is needed.
 
@@
 \subsubsection{Data Types}
-Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values.
-Sub-data types for numbers exist to explicitly define characteristics of the type of number represented.
-For example, Haskell has two types of integers: Int and Integer.
-Int has the system-defined maximum integer size as its range while Integer’s ranged is only bound by the available amount of memory, and thus re used for arbitrary precision integers.
-Haskell also has two floating point types: Float and Double, where a Double has twice the floating point precision of a Float.
+
+Haskell includes many of the data types that are standard in most languages, such as Integers, Floats, Characters, and Boolean values.
 
@@
 let c = 'c'
+let isHaskellAwesome = true
 \end{minted}
@@
 
-Haskell also has a String data type.
-Although Strings are represented by double quotations, they are actually stored as a list of characters.
-Thus, when specifiying a data type, String is equivalent to [Char].
+Haskell also allows the definition Strings, which are represented by surrounding text with double quotes.
+Strings, however, are not actually a data type.
+Although they can be initialized using the double quote syntax, the compiler converts the string into a list of characters at compile time.
+The use of the String notation is simply syntatic sugar for programmers.
+It also helps increase the readability of code.
+In the following example, the data is stored in the representation of str1: a list of characters.
+However, Haskell allows the definition of a string using double quotes, as seen in str2, which is much more understandable.
 
@@
 let str1 = ['H','a','s','k','e','l','l','!']
-let str2 = "Haskell!" 	-- a string representation of str1
+let str2 = "Haskell!"
 \end{minted}

### 2013-04-21 examples/haskell/InfixPostfix.hs
Made a few stylistic changes in the source.

@@ -9,10 +9,9 @@
 -}
 
 module InfixPostfix
-( infixToPostfix
-, evaluatePostfix
-)
-where
+( infixToPostfix,
+evaluatePostfix
+) where
 
 import Data.List.Split
 

### 2013-04-21 projects/term_paper/paper.tex
Final update for 4/20
Added module code example.

@@
 
-If the context does not suggest the type, as in the example below, then an exception will result.
+If the context does not suggest the type, as in the example below, then an exception will result because the compiler cannot infer what the type is going to be and is unable to handle it.
 
@@
 \subsubsection{Modules}
+\begin{minted}{haskell}
+module addNums
+( addTwo
+, addThree
+, addFour
+) where
 
+addTwo :: (Num a) => a -> a
+addTwo x = x + 2
+
+addThree :: (Num a) => a -> a
+addThree x = x + 3
+
+addFour :: (Num a) => a -> a
+addFour x = x + 4
+\end{minted}
 \subsubsection{Exception Handling}

### 2013-04-21 projects/term_paper/paper.tex
Added Nick's citations.

@@
 
-In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description and evaluation of functions in mathematics (Haskell).
-Lambda calculus became the foundation for functional programming (``Haskell'').
-However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there became the need for a standard functional language to aid the spread of functional programming (Hudak 1).
-A meeting was held in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need (Hudak 1).
-The meeting resulted in the formation of a committee to design a standard functional language.
-In 1990, the committee produced their result: a consolidation of existing functional programming languages into an open standard, common language to be used for functional programming research: Haskell (Hudak 3).
+In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description 
+and evaluation of functions in mathematics. Lambda calculus became the foundation for functional programming~\cite{haskell-wiki}. 
+However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there 
+became the need for a standard functional language to aid the spread of functional programming. A meeting was held 
+in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need~\cite{hudak-hist}. The meeting 
+resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: 
+a consolidation of existing functional programming languages into an open standard, common language to be used for 
+functional programming research: Haskell~\cite{hudak-con}.
 
-Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming.
-It has a lambda as its logo to symbolize lambda calculus as its foundation.
-Today, Haskell is widely used in many different aspects of computing.
-From AT\&T's automated processing of abuse complaints in its network security division to the National Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of modern industry (``Haskell'').
+Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. It has a 
+lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
+of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
+Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of 
+modern industry~\cite{haskell-wiki}.
 
@@
 
-Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values.
-Every function acts independently of other functions and does not change the state of anything outside of its scope.
-This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as well as to permit parallel processing.
-In addition, functions do not have to be declared in a particular order since they all exist independently of one another.
+Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and 
+return values. Every function acts independently of other functions and does not change the state of anything outside 
+of its scope. This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as 
+well as to permit parallel processing. In addition, functions do not have to be declared in a particular order since 
+they all exist independently of one another.
 
@@
 \subsubsection{Scoping}
-\bi
-    \item Static
-\ei
+In Haskell, static scoping is employed for
 
@@
 \begin{minted}{haskell}
-module addNums
-( addTwo
-, addThree
-, addFour
+module myMod 
+( 
+addTwo,
+addThree,
+addFour
 ) where

### 2013-04-21 examples/haskell/InfixPostfixTest.hs
Added appendix to paper and moved Haskell files for project to src/ for relative import.

@@ -1,21 +1,0 @@
-import Test.HUnit
-import InfixPostfix
-
--- main method
-main = do
-    let test1 = TestCase (assertEqual "infixToPostfix Test 0" "3 4 2 5 ^ - * 6 +" (infixToPostfix "3 * ( 4 - 2 ^ 5 ) + 6"))
-    let test2 = TestCase (assertEqual "infixToPostfix Test 1" "3 2 1 2 + ^ ^" (infixToPostfix "3 ^ 2 ^ ( 1 + 2 )"))
-    let test3 = TestCase (assertEqual "infixToPostfix Test 2" "10 2 2 2 ^ ^ * 10 50 * +" (infixToPostfix "10 * ( 2 ^ 2 ^ 2 ) + 10 * 50"))
-    let test4 = TestCase (assertEqual "infixToPostfix Test 3" "100 50 2 3 ^ - / 50 10 / - 5 +" (infixToPostfix "100 / ( 50 - 2 ^ 3 ) - 50 / 10 + 5"))
-    let test5 = TestCase (assertEqual "infixToPostfix Test 4" "10 54 10 % 25 10 - 2 2 ^ + * 3 / +" (infixToPostfix "10 + 54 % 10 * ( 25 - 10 + 2 ^ 2 ) / 3"))
-    let test6 = TestCase (assertEqual "infixToPostfix Test 5" "10 5 2 % + 5 3 3 ^ * + 25 5 / -" (infixToPostfix "( 10 + 5 % 2 ) + ( 5 * 3 ^ 3 ) - ( 25 / 5 )"))
-
-    let test7 = TestCase(assertEqual "evaluatePostfix Test 0" "-78" (evaluatePostfix "3 4 2 5 ^ - * 6 +"))
-    let test8 = TestCase(assertEqual "evaluatePostfix Test 1" "6561" (evaluatePostfix "3 2 1 2 + ^ ^"))
-    let test9 = TestCase(assertEqual "evaluatePostfix Test 2" "660" (evaluatePostfix "10 2 2 2 ^ ^ * 10 50 * +"))
-    let test10 = TestCase(assertEqual "evaluatePostfix Test 3" "2" (evaluatePostfix "100 50 2 3 ^ - / 50 10 / - 5 +"))
-    let test11 = TestCase(assertEqual "evaluatePostfix Test 4" "35" (evaluatePostfix "10 54 10 % 25 10 - 2 2 ^ + * 3 / +"))
[…]

### 2013-04-21 projects/term_paper/src/InfixPostfix.hs

@@ -21,7 +21,8 @@ infixToPostfix expr =
     let concatHigherPrec :: [String] -> String -> String
         concatHigherPrec [] _ = ""
         concatHigherPrec (x:xs) y
-            | (stackPrec x) >= (inputPrec y) = x ++ " " ++ (concatHigherPrec xs y)
+            | (stackPrec x) >= (inputPrec y) = x ++ " "
+                ++ (concatHigherPrec xs y)
             | otherwise = ""
 
         keepLowerPrec :: [String] -> String -> [String]
@@ -32,18 +33,24 @@ infixToPostfix expr =
 
         concatBeforeLeftParen :: [String] -> String
         concatBeforeLeftParen ("(":xs) = ""
-        concatBeforeLeftParen (x:xs) = x ++ " " ++ (concatBeforeLeftParen xs)
+        concatBeforeLeftParen (x:xs) = x ++ " "
+            ++ (concatBeforeLeftParen xs)
 
         removeToLeftParen :: [String] -> [String]
         removeToLeftParen ("(":xs) = xs
         removeToLeftParen (x:xs) = removeToLeftParen xs
 
-        parseExpr [] stack = (foldl (++) "" (zipWith (++) stack (replicate (length stack - 1) " "))) ++ (last stack)
+        parseExpr [] stack = 
+            (foldl (++) "" (zipWith (++) stack (replicate (length stack - 1) " ")))
+            ++ (last stack)
         parseExpr (x:xs) stack
             | isOperand x = x ++ " " ++ (parseExpr xs stack)
             | isLeftParen x = (parseExpr xs (x:stack))
-            | isOperator x = (concatHigherPrec stack x) ++ (parseExpr xs (x:(keepLowerPrec stack x)))
-            | (isRightParen x) && ("(" `elem` stack) = (concatBeforeLeftParen stack) ++ (parseExpr xs (removeToLeftParen stack))
+            | isOperator x = (concatHigherPrec stack x)
+                ++ (parseExpr xs (x:(keepLowerPrec stack x)))
+            | (isRightParen x) && ("(" `elem` stack) =
+                (concatBeforeLeftParen stack)
+                ++ (parseExpr xs (removeToLeftParen stack))
             | otherwise = error "Not a valid identifier: " ++ x
 
     in parseExpr (splitOn [' '] expr) []
@@ -55,7 +62,8 @@ evaluatePostfix expr = (parsePostfixExp (splitOn [' '] expr) [])
[…]

### 2013-04-21 projects/term_paper/src/InfixPostfixTest.hs

@@ -1,0 +1,47 @@
+import Test.HUnit
+import InfixPostfix
+
+-- main method
+main = do
+    let test1 = TestCase (assertEqual 
+                "infixToPostfix Test 0" "3 4 2 5 ^ - * 6 +"
+                (infixToPostfix "3 * ( 4 - 2 ^ 5 ) + 6"))
+    let test2 = TestCase (assertEqual 
+                "infixToPostfix Test 1" "3 2 1 2 + ^ ^"
+                (infixToPostfix "3 ^ 2 ^ ( 1 + 2 )"))
+    let test3 = TestCase (assertEqual
+                "infixToPostfix Test 2" "10 2 2 2 ^ ^ * 10 50 * +"
+                (infixToPostfix "10 * ( 2 ^ 2 ^ 2 ) + 10 * 50"))
+    let test4 = TestCase (assertEqual
+                "infixToPostfix Test 3" "100 50 2 3 ^ - / 50 10 / - 5 +"
+                (infixToPostfix "100 / ( 50 - 2 ^ 3 ) - 50 / 10 + 5"))
+    let test5 = TestCase (assertEqual
+                "infixToPostfix Test 4" "10 54 10 % 25 10 - 2 2 ^ + * 3 / +"
+                (infixToPostfix "10 + 54 % 10 * ( 25 - 10 + 2 ^ 2 ) / 3"))
+    let test6 = TestCase (assertEqual
+                "infixToPostfix Test 5" "10 5 2 % + 5 3 3 ^ * + 25 5 / -"
+                (infixToPostfix "( 10 + 5 % 2 ) + ( 5 * 3 ^ 3 ) - ( 25 / 5 )"))
+
+    let test7 = TestCase(assertEqual
+                "evaluatePostfix Test 0" "-78"
+                (evaluatePostfix "3 4 2 5 ^ - * 6 +"))
+    let test8 = TestCase(assertEqual
+                "evaluatePostfix Test 1" "6561"
+                (evaluatePostfix "3 2 1 2 + ^ ^"))
+    let test9 = TestCase(assertEqual 
+                "evaluatePostfix Test 2" "660"
+                (evaluatePostfix "10 2 2 2 ^ ^ * 10 50 * +"))
+    let test10 = TestCase(assertEqual
+                "evaluatePostfix Test 3" "2" 
+                (evaluatePostfix "100 50 2 3 ^ - / 50 10 / - 5 +"))
+    let test11 = TestCase(assertEqual
+                "evaluatePostfix Test 4" "35"
[…]

### 2013-04-21 projects/term_paper/paper.tex
Added appendix to paper and moved Haskell files for project to src/ for relative import.
Added more iteration examples.

@@
 
+\usepackage{appendix}
 \usepackage{minted}
@@
 \begin{minted}{haskell}
-myExp =
+myExp :: Float -> Float
+myExp x =
     let e = 2.7182
@@
     \item Map/fold
+\begin{minted}{haskell}
+sumSquares :: (Num a) => [a] -> a
+sumSquares xs = foldr1 (+) (map (**2) xs)
+\end{minted}
     \item Recursion
+\begin{minted}{haskell}
+countdown :: Int -> String
+countdown 0 = "Blast-off!"
+countdown x = (show x) ++ "...\n" ++ countdown (x-1)
+\end{minted}
 \ei
@@
 
+\newpage
+\begin{appendices}
+\section{Project Implementation in Haskell}
+\inputminted{haskell}{src/InfixPostfix.hs}
+\newpage
+\inputminted{haskell}{src/InfixPostfixTest.hs}
+\end{appendices}
+
+\newpage
 \bibliographystyle{abbrv}

### 2013-04-22 projects/term_paper/paper.tex
Added material on introspection and reflection.

@@
 \section{Introduction}
-This paper provides an overview of the Haskell programming language.
+This paper provides an overview of the Haskell programming language.  The sections are outlined as follows:
+section 1 describes the background surrounding Haskell, including its connections to functional programming,
+and its usage today.  Section 2 provides a survey of many of the data and control constructs native to Haskell.
+Section 3 presents a brief look at several extensions beyond the Haskell core.
 
@@
 (*) :: (Num a) => a -> a -> a
-(*) a b = a * a * b
+(*) a b = a + a + a + a
 print (2 * 3)
@@
 \subsubsection{Scoping}
-In Haskell, static scoping is employed for
+In Haskell, static scoping is employed.  As such, bindings are localized
+to the function in which they were defined or passed.
 
@@
 \section{Advanced Topics}
+Beyond the basic data and control structures discussed to this point,
+Haskell contains a wide array of constructs, extension modules, and
+and other features.  This section considers the following advanced
+topics: inheritance, concurrency, and runtime type checking.
 
 \subsection{Inheritance}
+
 \subsection{Concurrency Support}
-\subsection{Introspection}
+
+\subsection{Introspection and Reflection}
+As mentioned previously, Haskell posesses a strong static type system
+implented at compile time. As such, the Haskell '98 language definition
+does not provide support for runtime type examination or manipulation
+(i.e., introspection and reflection, respectively).  However, effors have been
+made toward adding support similar to these features:
+\bi
+    \item Scrap your boilerplate: generic programming~\cite{haskell-syb}
+    \item Template Haskell: an extension module for compile-time metaprogramming~\cite{haskell-th}
+\ei
 

### 2013-04-22 projects/term_paper/paper.tex
Merged our work

@@
 
-\usepackage{appendix}
 \usepackage{minted}
@@
 \section{Introduction}
-This paper provides an overview of the Haskell programming language.  The sections are outlined as follows:
-section 1 describes the background surrounding Haskell, including its connections to functional programming,
-and its usage today.  Section 2 provides a survey of many of the data and control constructs native to Haskell.
-Section 3 presents a brief look at several extensions beyond the Haskell core.
+This paper provides an overview of the Haskell programming language.
 
@@
 
-In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description 
-and evaluation of functions in mathematics. Lambda calculus became the foundation for functional programming~\cite{haskell-wiki}. 
-However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there 
-became the need for a standard functional language to aid the spread of functional programming. A meeting was held 
-in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need~\cite{hudak-hist}. The meeting 
-resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: 
-a consolidation of existing functional programming languages into an open standard, common language to be used for 
-functional programming research: Haskell~\cite{hudak-con}.
-
-Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. It has a 
-lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
-of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
-Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of 
-modern industry~\cite{haskell-wiki}.
+In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description and evaluation of functions in mathematics (Haskell).
+Lambda calculus became the foundation for functional programming (``Haskell'').
+However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there became the need for a standard functional language to aid the spread of functional programming (Hudak 1).
+A meeting was held in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need (Hudak 1).
+The meeting resulted in the formation of a committee to design a standard functional language.
+In 1990, the committee produced their result: a consolidation of existing functional programming languages into an open standard, common language to be used for functional programming research (Hudak 3).
+They named this language Haskell after Haskell Curry, a logician whose work greatly contributed to functional programming,
+and chose the lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects of computing.
 
@@
 
-Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and 
-return values. Every function acts independently of other functions and does not change the state of anything outside 
-of its scope. This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as 
-well as to permit parallel processing. In addition, functions do not have to be declared in a particular order since 
-they all exist independently of one another.
+Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and return values.
+Every function acts independently of other functions and does not change the state of anything outside of its scope.
+This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as well as to permit parallel processing.
+In addition, functions do not have to be declared in a particular order since they all exist independently of one another.
 
 \subsection{Application Domains}
+
+Haskell is most commonly used for the development of substantial software systems.
+The language is designed to produce productivity from programmers in fewer lines of code.
+In addition, having no side-effects leads to fewer errors.
+These features are very important in the development of large software systems, and Haskell is an ideal choice.
+
+Other popular uses of Haskell include the development of domain specific languages, web startups, mathematics, hardware design firms, finance, and aerospace and defense.
+Haskell's use in commercial industry ranges from AT\&T's automated processing of abuse complaints to the National Radio Astronomy Observatory’s implementation of core science algorithms.
 
@@
 Typeclasses can be used to allow multiple types to be passed to a function.
-For example, to create a function that will accept both Int and Integer types, it's as simple as declaring its typeclass as Integral.
+In the following example, the function declares its typeclass as Integral.
+Therefore, the function will allow accept Int or Integer types as parameters.
+
+\begin{minted}{haskell}
+incrementMe :: (Integral a) => a -> a
+incrementMe a = a + 1
+\end{minted}
 
@@
 \subsubsection{Expressions}
-\bi
-    \item Function definitions
+
+Function definitions in Haskell are very simple and straightforward.
+A function consists of the function name, parameters, and an expression.
+The return value of the function is the evaluation of the expression, which uses the parameters.
+The naming standard for functions in Haskell is to use camel case.
+All functions in Haskell must take at least one parameter and must return only one value.
+They can, however, be passed multiple parameters.
+Functions are usually called with prefix notation; that is, the name of the function is followed by its arguments.
+It is possible, however, to call functions using infix notation, which is sometimes appropriate if the function takes two arguments.
+Additionally, all operators are called using infix notation.
+The following example demonstrates how a function can be called using infix notation.
+
+\begin{minted}{haskell}
+let evens = [2, 4, 6, 8]
+print (elem 2 evens)   -- prefix notation
+print (2 `elem` evens) -- infix  notation
+\end{minted}
+
+The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list is the return type.
+The following function is called ``greet."
+It takes in a string and returns a string.
+The string is passed in as the variable ``name." Everything that follows the equal sign is the expression, and the evaluation of this expression is the return value.
+
 \begin{minted}{haskell}
@@
 \end{minted}
-    \item Bindings: let/in (valid expression), where (locally bound to a syntactic construct)
+
+Bindings in Haskell can be created in two different ways.
+The first is using `where' bindings.
+Where bindings allow the definition of a function inside another function.
+The scope of the function declared by a where is locally bound by the function that created it.
+Functions outside of the declaring function cannot call the function declared inside the where.
+Additionally, where bindings can be nested; that is, a function declared inside a where can declare its own helper functions inside a where.
+Where bindings can also span across guards, which have not been discussed yet.
+
+In the following example, the function rectPrismVol declares two functions: faceArea and baseArea. Only the rectPrismVol function is allowed to call these functions because they are locally bound.
+
 \begin{minted}{haskell}
@@
 \end{minted}
+
+The second type of binding available in Haskell is done using `let' bindings.
+Let bindings allow the declaration of variables that are expressions themselves and are locally bound.
+Let bindings are often used for pattern matching.
+The syntax of let bindings involved declaring the bindings inside a `let' declaration, followed by defining an expression inside an `in' declaration.
+The let and in statements must be aligned in the same column.
+
 \begin{minted}{haskell}
-myExp :: Float -> Float
-myExp x =
+myExp =
     let e = 2.7182
@@
 \end{minted}
-NOTE: statements in let/in must be aligned in same column
-\ei
+
+The difference between let and where bindings is that let bindings are expressions themselves, whereas where bindings are just syntactic constructs.
+Additionally, unlike where bindings, let bindings cannot span across guards, a feature that has not yet been discussed.
 
 \subsubsection{Operators and Precedence}
-\bi
-    \item Operators: postfix notation, naming typically consists of symbols
-    \item Functions: infix notation, named using alphanumeric characters in camel case
-    \item Any function can be used as an operator by calling it in postfix notation
+
+Operators in Haskell are typically represented with symbols.
+Some of the basic operators in Haskell include addition, subtraction, multiplication, divison, exponentiation, concatenation, and equality operators and logic operators.
+The precedence of operators conform to the standard orders used in mathematics: exponentiation is highest, followed by muliplication and visision, with addition and subtraction with the lowest precedence.
+
+All operators in Haskell take two arguments, and they are usually called using infix notation; that is, the operator is placed between its two arguments.
+Although it is possible to use operators in prefix notation, it is customary to use infix notation to increase readability.
+This contrasts from most functional programming languages.
+
 \begin{minted}{haskell}
-f :: (Int a) => a -> a -> a
-f a b = a + b
-; invoke the function in postfix notation
-print (1 `f` 2)
+print (2 + 5)    -- infix notation is the standard
+print ((+) 2 5)  -- prefix notation is still possible
 \end{minted}
-    \item Any operator can be called as a function in infix notation
-\begin{minted}{haskell}
-print ((+) 2 5)
-\end{minted}
-    \item Operators can be overloaded
+
+Operators in Haskell can also be overloaded. The number and type of arguments as well as the expression can be modified.
+
 \begin{minted}{haskell}
 (*) :: (Num a) => a -> a -> a
-(*) a b = a + a + a + a
-print (2 * 3)
+(*) a b = a * a * b
+print (2 * 3)   -- this yields 12 rather than 6
 \end{minted}
-\ei
 
 \subsubsection{Selection Constructs}
-\bi
-    \item Pattern matching
+
+Selection constructs in Haskell consist of if-else statements, guards, pattern matching, and case expressions.
+
+If-else statements in Haskell conform to the traditional syntax of the if-else selection construct.
+The only notable difference is that Haskell requires that every conditional is followed by a then expression and an else expression.
+The compiler will prevent compilation for any if conditional that does not also have then and else statements because without them it would be possible for an input to cause a function not to have a return value, which Haskell does not allow.
+
+\begin{minted}{haskell}
+guessGame :: Int -> String
+guessGame x = if x == 42
+    then "You have a deep understanding of life."
+    else "You need to think more about life."
+\end{minted}
+
+If-else statements are not used in Haskell as often as they are in imperative languages because Haskell offers a feature known as guards, which are fundamentally equivalent to if-else statements except they are much more easily understood, work with multiple conditions, and blend well with pattern matching.
+Guards are created using pipes in the expression of a function and consist of a conditional, which must evaluate to true or false, and an expression.
+An equals sign separates the conditional from the expression.
+Arguments are checked against the guards in sequential order.
+If the condition is true, then the expression for that guard is evaluated and returned.
+If the condition is false, then the next guard condition is evaluated, and this pattern continues until the `otherwise' guard is reached, which catches all input that did not match any guard previous conditions.
+The following function has three guards, each following a pipe.
+A notable aspect of this function is that if the input is value is greater than 100,000 it will cause the first guard condition to be true and will evaluate the first guard expression even though the input would also be true for the second guard.
+This is because the guards are checked in order, so the second guard is never checked because the first guard is true and the return value is determined from it.
+The otherwise guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
+
+\begin{minted}{haskell}
+let balance = 200
+assessWorth :: Int -> String
+assessWorth =
+    | balance > 100000 = "You're rich!"
+    | balance > 100 = "You're rich by student standards!"
+    | otherwise = "Need a loan, friend?"
+\end{minted}
+
+Another selection construct in Haskell is pattern matching.
+Pattern matching is a simple way to have a function perform differently based on its input.
+It is initiatiated by defining a function multiple times in a row using patterns as parameters.
+The final declaration of the function must use a variable for the parameter in case the input does not match a pattern.
+The function will check the input against the patterns in order from first declared to last; thus, if the input does not conform to the first pattern, it will move on to the next pattern, and so on.
+
+In the following example, an input of ``Haskell" will produce the first expression, ``Clojure" will skip the first and produce the second, and any other input will produce the third.
+Note that the third and final expression does not have a pattern to match, but instead uses a variable to catch all other input.
+
 \begin{minted}{haskell}
@@
 \end{minted}
-    \item if/then/else
-\begin{minted}{haskell}
-guessGame :: Int -> String
-guessGame x = if x == 42
-    then "You have a deep understanding of life."
-    else "You need to think more about life."
-\end{minted}
-    \item Guards
-\begin{minted}{haskell}
-let balance = 200
-assessWorth :: Int -> String
-assessWorth =
-    | balance >= 100000 = "You're rich!"
-    | balance >= 100 = "You're rich by student standards!"
-    | otherwise = "Need a loan, friend?"
-\end{minted}
-    \item Case expression
+
+The final selection construct in Haskell is case expressions.
+Case expressions evaluate expressions based on the possible cases of a value.
+They are similar to the standard use of cases, except they can also pattern match the input.
+Note that this is exactly how pattern matching parameters in function definitions works.
+In fact, pattern matching parameters is simply an easier way to write case expressions, and the two are interchangeable.
+
+The following function demonstrates how to evaluate a specific expression that depends on which pattern an argument matches by using the `case' construct.
+Note that if this function were written using the pattern matching technique it would work exactly the same way and the code would be more readable.
+
 \begin{minted}{haskell}
@@
 \end{minted}
-\ei
 

### 2013-04-22 projects/term_paper/paper.tex
Done merging. Getting an error when converting to pdf
Fixed merger issues.

@@
 
-In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description and evaluation of functions in mathematics (Haskell).
-Lambda calculus became the foundation for functional programming (``Haskell'').
-However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there became the need for a standard functional language to aid the spread of functional programming (Hudak 1).
-A meeting was held in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need (Hudak 1).
-The meeting resulted in the formation of a committee to design a standard functional language.
-In 1990, the committee produced their result: a consolidation of existing functional programming languages into an open standard, common language to be used for functional programming research (Hudak 3).
-They named this language Haskell after Haskell Curry, a logician whose work greatly contributed to functional programming,
-and chose the lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects of computing.
+In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description 
+and evaluation of functions in mathematics. Lambda calculus became the foundation for functional programming~\cite{haskell-wiki}. 
+However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there 
+became the need for a standard functional language to aid the spread of functional programming. A meeting was held 
+in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need~\cite{hudak-hist}. The meeting 
+resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: 
+a consolidation of existing functional programming languages into an open standard, common language to be used for 
+functional programming research: Haskell~\cite{hudak-con}.
+
+Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. It has a 
+lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
+of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
+Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of 
+modern industry~\cite{haskell-wiki}.
 

### 2013-04-22 projects/term_paper/paper.tex
Fixed a few typos.

@@
 
-Haskell is most commonly used for the development of substantial software systems.
-The language is designed to produce productivity from programmers in fewer lines of code.
-In addition, having no side-effects leads to fewer errors.
+Haskell is most commonly used for the development of substantial software systems. The language is designed to produce
+productivity from programmers in fewer lines of code. In addition, having no side-effects leads to fewer errors.
 These features are very important in the development of large software systems, and Haskell is an ideal choice.
 
-Other popular uses of Haskell include the development of domain specific languages, web startups, mathematics, hardware design firms, finance, and aerospace and defense.
-Haskell's use in commercial industry ranges from AT\&T's automated processing of abuse complaints to the National Radio Astronomy Observatory’s implementation of core science algorithms.
+Other popular uses of Haskell include the development of domain specific languages, web startups, mathematics, 
+hardware design firms, finance, and aerospace and defense. Haskell's use in commercial industry ranges from AT\&T's 
+automated processing of abuse complaints to the National Radio Astronomy Observatory’s implementation of core science algorithms.
 
@@
 
-Two more essential data types in Haskell are lists and tuples.
-Lists are the most used data type due to their expendability and the wide range of functions that are available to manipulate them.
-They can easily be created, traversed, concatenated, reversed, sorted, and more with standard, built-in functions.
-Lists, however, are homogeneous and can only contain elements of the same data type.
-Tuples, on the other hand, can be heterogeneous.
-They are useful when the types and exact number of values to be combined are known.
-Like lists, tuples also comes with a surplus of built-in functions, one of which is the ability to zip two lists into one by joining matching elements into pairs.
-Simple yet elegant code can be written which combines the attributes of lists, tuples, and the other various other data types in Haskell.
+Two more essential data types in Haskell are lists and tuples. Lists are the most used data type due to their expendability 
+and the wide range of functions that are available to manipulate them. They can easily be created, traversed, concatenated, 
+reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous and can only contain elements 
+of the same data type. Tuples, on the other hand, can be heterogeneous. They are useful when the types and exact number of 
+values to be combined are known. Like lists, tuples also comes with a surplus of built-in functions, one of which is the 
+ability to zip two lists into one by joining matching elements into pairs. Simple yet elegant code can be written which 
+combines the attributes of lists, tuples, and the other various other data types in Haskell.
 
@@
 
-Haskell also allows the definition Strings, which are represented by surrounding text with double quotes.
-Strings, however, are not actually a data type.
-Although they can be initialized using the double quote syntax, the compiler converts the string into a list of characters at compile time.
-The use of the String notation is simply syntatic sugar for programmers.
-It also helps increase the readability of code.
-In the following example, the data is stored in the representation of str1: a list of characters.
-However, Haskell allows the definition of a string using double quotes, as seen in str2, which is much more understandable.
+Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
+are not actually a data type. Although they can be initialized using the double quote syntax, the compiler converts the 
+string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. 
+It also helps increase the readability of code. In the following example, the data is stored in the representation of 
+str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in str2, 
+which is much more understandable.
 
@@
 
-In addition to these basic data types, Haskell also offers type variables.
-Type variables are variables whose type has not been explicitly declared; rather, they can be any type.
-By defining a function without declaring data types, the variables in the function can be used as any type and the function can be polymorphic.
-In the following example, the function can handle a list of any type because its uses a type variable.
+In addition to these basic data types, Haskell also offers type variables. Type variables are variables whose type has 
+not been explicitly declared; rather, they can be any type. By defining a function without declaring data types, the 
+variables in the function can be used as any type and the function can be polymorphic. In the following example, the 
+function can handle a list of any type because its uses a type variable.
 
@@
 \subsubsection{Type Checking}
-Type checking in Haskell is performed statically at compile time.
-Haskell uses type-declarations for functions, in which the types of parameters and return values are explicitly defined.
-Any use of a function in which parameters do not meet the defined function type is flagged by the compiler, and compilation will be aborted.
-In addition, ues type inferencing by context.
-The type system in Haskell deduces obvious types and makes them concrete.
-In the following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type is desired because myNum is added to an Int.
+Type checking in Haskell is performed statically at compile time. Haskell uses type-declarations for functions, in 
+which the types of parameters and return values are explicitly defined. Any use of a function in which parameters 
+do not meet the defined function type is flagged by the compiler, and compilation will be aborted. In addition, 
+use type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
+following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type 
+is desired because myNum is added to an Int.
 
@@
 
-If the context does not suggest the type, as in the example below, then an exception will result because the compiler cannot infer what the type is going to be and is unable to handle it.
+If the context does not suggest the type, as in the example below, then an exception will result because the 
+compiler cannot infer what the type is going to be and is unable to handle it.
 
@@
 
-Haskell uses typeclasses to categorize the type system.
-Typeclasses define the behavior of a general type.
-A type must support the definition of its typeclass, but may also be more specific.
-For example, all of the operators in Haskell are categorized under the Eq typeclass.
-Other examples of typeclasses in Haskell include Ord, Show, Read, Enum, Num, Integral, and Floating.
-Typeclasses can be used to allow multiple types to be passed to a function.
-In the following example, the function declares its typeclass as Integral.
-Therefore, the function will allow accept Int or Integer types as parameters.
+Haskell uses typeclasses to categorize the type system. Typeclasses define the behavior of a general type. 
+A type must support the definition of its typeclass, but may also be more specific. For example, all of the 
+operators in Haskell are categorized under the Eq typeclass. Other examples of typeclasses in Haskell include Ord, 
+Show, Read, Enum, Num, Integral, and Floating. Typeclasses can be used to allow multiple types to be passed to a 
+function. In the following example, the function declares its typeclass as Integral. Therefore, the function will 
+allow accept Int or Integer types as parameters.
 
@@
 
-Function definitions in Haskell are very simple and straightforward.
-A function consists of the function name, parameters, and an expression.
-The return value of the function is the evaluation of the expression, which uses the parameters.
-The naming standard for functions in Haskell is to use camel case.
-All functions in Haskell must take at least one parameter and must return only one value.
-They can, however, be passed multiple parameters.
-Functions are usually called with prefix notation; that is, the name of the function is followed by its arguments.
-It is possible, however, to call functions using infix notation, which is sometimes appropriate if the function takes two arguments.
-Additionally, all operators are called using infix notation.
-The following example demonstrates how a function can be called using infix notation.
+Function definitions in Haskell are very simple and straightforward. A function consists of the function name, 
+parameters, and an expression. The return value of the function is the evaluation of the expression, which 
+uses the parameters. The naming standard for functions in Haskell is to use camel case. All functions in 
+Haskell must take at least one parameter and must return only one value. They can, however, be passed 
+multiple parameters. Functions are usually called with prefix notation; that is, the name of the function is 
+followed by its arguments. It is possible, however, to call functions using infix notation, which is sometimes appropriate 
+if the function takes two arguments. Additionally, all operators are called using infix notation. The following example 
+demonstrates how a function can be called using infix notation.
 
@@
 
-The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list is the return type.
-The following function is called ``greet."
+The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is 
+read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list 
+is the return type. The following function is called ``greet."
+
 It takes in a string and returns a string.
@@
 
-Bindings in Haskell can be created in two different ways.
-The first is using `where' bindings.
-Where bindings allow the definition of a function inside another function.
-The scope of the function declared by a where is locally bound by the function that created it.
-Functions outside of the declaring function cannot call the function declared inside the where.
-Additionally, where bindings can be nested; that is, a function declared inside a where can declare its own helper functions inside a where.
-Where bindings can also span across guards, which have not been discussed yet.
+Bindings in Haskell can be created in two different ways. The first is using `where' bindings. Where bindings allow 
+the definition of a function inside another function. The scope of the function declared by a where is locally bound 
+by the function that created it. Functions outside of the declaring function cannot call the function declared inside 
+the where. Additionally, where bindings can be nested; that is, a function declared inside a where can declare its 
+own helper functions inside a where. Where bindings can also span across guards, which have not been discussed yet.
 
-In the following example, the function rectPrismVol declares two functions: faceArea and baseArea. Only the rectPrismVol function is allowed to call these functions because they are locally bound.
+In the following example, the function rectPrismVol declares two functions: faceArea and baseArea. Only the rectPrismVol 
+function is allowed to call these functions because they are locally bound.
 
@@
 
-The second type of binding available in Haskell is done using `let' bindings.
-Let bindings allow the declaration of variables that are expressions themselves and are locally bound.
-Let bindings are often used for pattern matching.
-The syntax of let bindings involved declaring the bindings inside a `let' declaration, followed by defining an expression inside an `in' declaration.
-The let and in statements must be aligned in the same column.
+The second type of binding available in Haskell is done using `let' bindings. Let bindings allow the declaration of 
+variables that are expressions themselves and are locally bound. Let bindings are often used for pattern matching. 
+The syntax of let bindings involved declaring the bindings inside a `let' declaration, followed by defining an 
+expression inside an `in' declaration. The let and in statements must be aligned in the same column.
 
@@
 
-The difference between let and where bindings is that let bindings are expressions themselves, whereas where bindings are just syntactic constructs.
-Additionally, unlike where bindings, let bindings cannot span across guards, a feature that has not yet been discussed.
+The difference between let and where bindings is that let bindings are expressions themselves, whereas where 
+bindings are just syntactic constructs. Additionally, unlike where bindings, let bindings cannot span across guards, 
+a feature that has not yet been discussed.
 
@@
 
-Operators in Haskell are typically represented with symbols.
-Some of the basic operators in Haskell include addition, subtraction, multiplication, divison, exponentiation, concatenation, and equality operators and logic operators.
-The precedence of operators conform to the standard orders used in mathematics: exponentiation is highest, followed by muliplication and visision, with addition and subtraction with the lowest precedence.
+Operators in Haskell are typically represented with symbols. Some of the basic operators in Haskell include addition, 
+subtraction, multiplication, divison, exponentiation, concatenation, and equality operators and logic operators. The 
+precedence of operators conform to the standard orders used in mathematics: exponentiation is highest, followed by 
+muliplication and visision, with addition and subtraction with the lowest precedence.
 
-All operators in Haskell take two arguments, and they are usually called using infix notation; that is, the operator is placed between its two arguments.
-Although it is possible to use operators in prefix notation, it is customary to use infix notation to increase readability.
-This contrasts from most functional programming languages.
+All operators in Haskell take two arguments, and they are usually called using infix notation; that is, the operator is 
+placed between its two arguments. Although it is possible to use operators in prefix notation, it is customary to use 
+infix notation to increase readability. This contrasts from most functional programming languages.
 
@@
 
-If-else statements in Haskell conform to the traditional syntax of the if-else selection construct.
-The only notable difference is that Haskell requires that every conditional is followed by a then expression and an else expression.
-The compiler will prevent compilation for any if conditional that does not also have then and else statements because without them it would be possible for an input to cause a function not to have a return value, which Haskell does not allow.
+If-else statements in Haskell conform to the traditional syntax of the if-else selection construct. The only notable 
+difference is that Haskell requires that every conditional is followed by a then expression and an else expression. 
+The compiler will prevent compilation for any if conditional that does not also have then and else statements because 
+without them it would be possible for an input to cause a function not to have a return value, which Haskell does not allow.
 
@@
 
-If-else statements are not used in Haskell as often as they are in imperative languages because Haskell offers a feature known as guards, which are fundamentally equivalent to if-else statements except they are much more easily understood, work with multiple conditions, and blend well with pattern matching.
-Guards are created using pipes in the expression of a function and consist of a conditional, which must evaluate to true or false, and an expression.
-An equals sign separates the conditional from the expression.
-Arguments are checked against the guards in sequential order.
-If the condition is true, then the expression for that guard is evaluated and returned.
-If the condition is false, then the next guard condition is evaluated, and this pattern continues until the `otherwise' guard is reached, which catches all input that did not match any guard previous conditions.
-The following function has three guards, each following a pipe.
-A notable aspect of this function is that if the input is value is greater than 100,000 it will cause the first guard condition to be true and will evaluate the first guard expression even though the input would also be true for the second guard.
-This is because the guards are checked in order, so the second guard is never checked because the first guard is true and the return value is determined from it.
-The otherwise guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
+If-else statements are not used in Haskell as often as they are in imperative languages because Haskell offers a feature 
+known as guards, which are fundamentally equivalent to if-else statements except they are much more easily understood, 
+work with multiple conditions, and blend well with pattern matching. Guards are created using pipes in the 
+expression of a function and consist of a conditional, which must evaluate to true or false, and an expression. 
+An equals sign separates the conditional from the expression. Arguments are checked against the guards in 
+sequential order. If the condition is true, then the expression for that guard is evaluated and returned. 
+If the condition is false, then the next guard condition is evaluated, and this pattern continues until the 
+`otherwise' guard is reached, which catches all input that did not match any guard previous conditions. The 
+following function has three guards, each following a pipe. A notable aspect of this function is that if the 
+input is value is greater than 100,000 it will cause the first guard condition to be true and will evaluate the 
+first guard expression even though the input would also be true for the second guard. This is because the guards are 
+checked in order, so the second guard is never checked because the first guard is true and the return value is 
+determined from it. The otherwise guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
 
@@
 
-Another selection construct in Haskell is pattern matching.
-Pattern matching is a simple way to have a function perform differently based on its input.
-It is initiatiated by defining a function multiple times in a row using patterns as parameters.
-The final declaration of the function must use a variable for the parameter in case the input does not match a pattern.
-The function will check the input against the patterns in order from first declared to last; thus, if the input does not conform to the first pattern, it will move on to the next pattern, and so on.
+Another selection construct in Haskell is pattern matching. Pattern matching is a simple way to have a 
+function perform differently based on its input. It is initiatiated by defining a function multiple times in 
+a row using patterns as parameters. The final declaration of the function must use a variable for the parameter 
+in case the input does not match a pattern. The function will check the input against the patterns in order from 
+first declared to last; thus, if the input does not conform to the first pattern, it will move on to the next pattern, and so on.
 
-In the following example, an input of ``Haskell" will produce the first expression, ``Clojure" will skip the first and produce the second, and any other input will produce the third.
-Note that the third and final expression does not have a pattern to match, but instead uses a variable to catch all other input.
+In the following example, an input of ``Haskell'' will produce the first expression, ``Clojure'' will skip the first 
+and produce the second, and any other input will produce the third. Note that the third and final expression does 
+not have a pattern to match, but instead uses a variable to catch all other input.
 
@@
 
-The final selection construct in Haskell is case expressions.
-Case expressions evaluate expressions based on the possible cases of a value.
-They are similar to the standard use of cases, except they can also pattern match the input.
-Note that this is exactly how pattern matching parameters in function definitions works.
-In fact, pattern matching parameters is simply an easier way to write case expressions, and the two are interchangeable.
+The final selection construct in Haskell is case expressions. Case expressions evaluate expressions based on 
+the possible cases of a value. They are similar to the standard use of cases, except they can also pattern 
+match the input. Note that this is exactly how pattern matching parameters in function definitions works. In 
+fact, pattern matching parameters is simply an easier way to write case expressions, and the two are interchangeable.
 
-The following function demonstrates how to evaluate a specific expression that depends on which pattern an argument matches by using the `case' construct.
-Note that if this function were written using the pattern matching technique it would work exactly the same way and the code would be more readable.
+The following function demonstrates how to evaluate a specific expression that depends on which pattern 
+an argument matches by using the `case' construct. Note that if this function were written using the 
+pattern matching technique it would work exactly the same way and the code would be more readable.
 

### 2013-04-22 projects/term_paper/paper.tex
Edits up to section 2.1.1.

@@
 and evaluation of functions in mathematics. Lambda calculus became the foundation for functional programming~\cite{haskell-wiki}. 
-However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there 
-became the need for a standard functional language to aid the spread of functional programming. A meeting was held 
+However, as numerous functional languages began to develop, many exhibited similar expressiveness and semantics.  This led to
+desire for a standard functional language to aid the spread of functional programming. A meeting was held 
 in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need~\cite{hudak-hist}. The meeting 
-resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: 
-a consolidation of existing functional programming languages into an open standard, common language to be used for 
+resulted in the formation of a committee to design a standard functional language. In 1990, the committee performed 
+a consolidation of the aspects of existing functional programming languages into an open standard, common language to be used for 
 functional programming research: Haskell~\cite{hudak-con}.
 
-Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. It has a 
-lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
+Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. The logo of Haskell, lambda,
+symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
 of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
@@
 
-Haskell is a pure functional language, which means that its functions cannot change values, but rather only accept and 
-return values. Every function acts independently of other functions and does not change the state of anything outside 
-of its scope. This is referred to as having no "side-effects," and it allows Haskell to be exceptionally optimized as 
-well as to permit parallel processing. In addition, functions do not have to be declared in a particular order since 
-they all exist independently of one another.
+The core of Haskell is a pure functional language, which means that its functions possess no concept of memory locations or other
+hardware-related statefullness. Every function acts independently of other functions and does not change the state of anything outside 
+its scope. This concept is referred to as having no ``side-effects,'' and this affords Haskell a certain simplicity in design
+and implementation, as well as lends itself to other means such as optimization toward parallel processing. In addition,
+functions do not have to be declared in a particular order since they all exist independently of one another.
 
@@
 
-[TODO]~\cite{learnyouahaskell}
+\section{Data and Control Abstractions}
+This section presents a tutorial-style introduction to the core concepts of
+the Haskell language~\cite{learnyouahaskell}.  Data and control abstractions are covered
+in the proceeding sections.  To begin with, the obligatory ``Hello, World!'' program is Haskell
+is presented below.
+
 \begin{minted}{haskell}
 module Main where
-import Data.List
 
 main :: IO ()
-main = putStrLn "Hello World!" >> test
-
-test = do 
-    print 123
+main = putStrLn "Hello World!"
 \end{minted}
 
-\section{Data and Control Abstractions}
+\subsection{Data Abstractions}
+Haskell supports a very rich, strong, static type system for programmers.  As Haskell is
+a compiled language, with the Glasgow Haskell Compiler (GHC) being the most common implementation,
+most of the type checking is done and enforced at compile time.
 
-\subsection{Data Abstractions}
 \subsubsection{Data Types}

### 2013-04-22 projects/term_paper/paper.tex
Added Nick's section on inheritance.

@@
 
+Inheritance in Haskell can be achieved through class extension, which involves a class defined as a subclass 
+of another class. The subclass then inherits all of the operations in the superclass. A benefit to class 
+extension is shorter contexts: a type expression for a function that uses operations from both the subclass 
+and the superclass only has to use the context of the subclass. Additionally, methods for subclass 
+operations can assume the existence of methods for superclass operations.
+
+The following class definition of Ord inherits all of the operations in Eq, but also includes the comparison 
+operators as well as maximum and minimum functions.
+
+\begin{minted}{haskell}
+class  (Eq a) => Ord a  where
+    (<), (<=), (>=), (>)  :: a -> a -> Bool
+    max, min              :: a -> a -> a
+\end{minted}
+
 \subsection{Concurrency Support}
@@
 \subsection{Introspection and Reflection}
+
 As mentioned previously, Haskell posesses a strong static type system

### 2013-04-22 projects/term_paper/paper.tex
Fixed a small typo in a code example.
Edits through 2.1.2, and fixed some code examples.

@@
 let c = 'c'
-let isHaskellAwesome = true
+let isHaskellAwesome = True
 \end{minted}
 
-Two more essential data types in Haskell are lists and tuples. Lists are the most used data type due to their expendability 
+Two more foundational data types in Haskell are lists and tuples. Lists are the most used data type due to their expendability 
 and the wide range of functions that are available to manipulate them. They can easily be created, traversed, concatenated, 
-reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous and can only contain elements 
-of the same data type. Tuples, on the other hand, can be heterogeneous. They are useful when the types and exact number of 
-values to be combined are known. Like lists, tuples also comes with a surplus of built-in functions, one of which is the 
-ability to zip two lists into one by joining matching elements into pairs. Simple yet elegant code can be written which 
-combines the attributes of lists, tuples, and the other various other data types in Haskell.
+reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous, ordered collections of
+similar data types. Tuples, on the other hand, heterogeneous collections. Tuples are most useful when the types and exact number of 
+values to be combined are known. Like lists, there is a wide array of built-in functions for tuples including, for instance,
+a function for zipping two lists into one by joining matching elements into tuples. Simple yet elegant code can be written by
+employing lists, tuples, and the other various other data types in Haskell.
 
@@
 Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
-are not actually a data type. Although they can be initialized using the double quote syntax, the compiler converts the 
+are not their own data type. Although string literals can be initialized using the double quote syntax, the compiler converts the 
 string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. 
 It also helps increase the readability of code. In the following example, the data is stored in the representation of 
-str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in str2, 
+str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in \texttt{str2}, 
 which is much more understandable.
@@
 let str1 = ['H','a','s','k','e','l','l','!']
-let str2 = "Haskell!"
+let str2 = "Haskell!"   -- shorthand for str1
 \end{minted}
@@
 not been explicitly declared; rather, they can be any type.  By defining a function without declaring data types, the 
-variables in the function can be used as any type and the function can be polymorphic. In the following example, the 
+variables in the function can be used as any type thereby enabling polymorphic behaviors. In the following example, the 
 function can handle a list of any type because its uses a type variable.

### 2013-04-22 projects/term_paper/paper.tex
Standardized code references and made a few edits through 2.2.2.

@@
 
-The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is 
-read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list 
-is the return type. The following function is called ``greet."
+The data type for each parameter of a function can be explicitly declared by using the \texttt{::} symbol, which is 
+read as ``has a type of.''  The types of the parameters can be listed in order, and the last type in the list 
+is the return type. The following function is called \texttt{greet}.
 
-It takes in a string and returns a string.
-The string is passed in as the variable ``name." Everything that follows the equal sign is the expression, and the evaluation of this expression is the return value.
+It takes in a string and returns a string. The string is passed in as the variable \texttt{name}. Everything that follows 
+the equal sign is the expression, and the evaluation of this expression is the return value.
 
@@
 
-Bindings in Haskell can be created in two different ways. The first is using `where' bindings. Where bindings allow 
-the definition of a function inside another function. The scope of the function declared by a where is locally bound 
+Bindings in Haskell can be created in two different ways. The first is using \texttt{where} bindings. \texttt{where} bindings allow 
+the definition of a function inside another function. The scope of the function declared by a \texttt{where} is locally bound 
 by the function that created it. Functions outside of the declaring function cannot call the function declared inside 
-the where. Additionally, where bindings can be nested; that is, a function declared inside a where can declare its 
-own helper functions inside a where. Where bindings can also span across guards, which have not been discussed yet.
+the \texttt{where}. Additionally, \texttt{where} bindings can be nested; that is, a function declared inside a \texttt{where} can declare
+its own helper functions inside a \texttt{where}. \texttt{where} bindings can also span across guards, which will be covered shortly.
 
-In the following example, the function rectPrismVol declares two functions: faceArea and baseArea. Only the rectPrismVol 
-function is allowed to call these functions because they are locally bound.
+In the following example, the function \texttt{rectPrismVol} declares two functions: \texttt{faceArea} and \texttt{baseArea}. Only the 
+\texttt{rectPrismVol} function is allowed to call these functions because they are locally bound.
 
@@
 
-The second type of binding available in Haskell is done using `let' bindings. Let bindings allow the declaration of 
-variables that are expressions themselves and are locally bound. Let bindings are often used for pattern matching. 
-The syntax of let bindings involved declaring the bindings inside a `let' declaration, followed by defining an 
-expression inside an `in' declaration. The let and in statements must be aligned in the same column.
+The second type of binding available in Haskell is done using \texttt{let} bindings. \texttt{let} bindings allow the declaration of 
+variables that are expressions themselves and are locally bound.  \texttt{let} bindings are often used for pattern matching. 
+The syntax of \texttt{let} bindings involved declaring the bindings inside a \texttt{let} declaration, followed by defining an 
+expression inside an \texttt{in} declaration. The \texttt{let} and \texttt{in} statements must be aligned in the same column.
 
@@
 
-The difference between let and where bindings is that let bindings are expressions themselves, whereas where 
-bindings are just syntactic constructs. Additionally, unlike where bindings, let bindings cannot span across guards, 
-a feature that has not yet been discussed.
+The difference between \texttt{let} and \texttt{where} bindings is that \texttt{let} bindings are expressions themselves, whereas 
+\texttt{where} bindings are just syntactic constructs. Additionally, unlike \texttt{where} bindings, \texttt{let} bindings cannot 
+span across guards.
 
@@
 
-All operators in Haskell take two arguments, and they are usually called using infix notation; that is, the operator is 
+All operators in Haskell are binary, and they are usually called using infix notation; that is, the operator is 
 placed between its two arguments. Although it is possible to use operators in prefix notation, it is customary to use 
@@
 (*) :: (Num a) => a -> a -> a
-(*) a b = a * a * b
-print (2 * 3)   -- this yields 12 rather than 6
+(*) a b = a + a + a + a
+print (2 * 3)   -- yields 8 rather than 6
 \end{minted}

### 2013-04-22 projects/term_paper/paper.tex
More edits.

@@
 
-Another selection construct in Haskell is pattern matching. Pattern matching is a simple way to have a 
-function perform differently based on its input. It is initiatiated by defining a function multiple times in 
-a row using patterns as parameters. The final declaration of the function must use a variable for the parameter 
-in case the input does not match a pattern. The function will check the input against the patterns in order from 
-first declared to last; thus, if the input does not conform to the first pattern, it will move on to the next pattern, and so on.
+Another selection construct in Haskell is pattern matching. Pattern matching is simply a way to have a 
+function perform different actions based on its input. Pattern matching is done by defining a function multiple times in 
+succession using patterns in place of parameters.  When the function is called, its arguments are checked against all patterns,
+starting with the first and proceeding accordingly.  If no match is made, an exception is raised.
+A default match can be speficied by listing `plain' variables as function parameters.
 

### 2013-04-22 projects/term_paper/paper.tex
Edits on section 3.

@@
 The final selection construct in Haskell is case expressions. Case expressions evaluate expressions based on 
-the possible cases of a value. They are similar to the standard use of cases, except they can also pattern 
+the values of a parameter. They are similar to case constructs in imperative languages, except they can also pattern 
 match the input. Note that this is exactly how pattern matching parameters in function definitions works. In 
@@
 The following function demonstrates how to evaluate a specific expression that depends on which pattern 
-an argument matches by using the `case' construct. Note that if this function were written using the 
-pattern matching technique it would work exactly the same way and the code would be more readable.
+an argument matches by using the \texttt{case} construct. Note that if this function were written using the 
+pattern matching technique it would work exactly the same way.
 
@@
 
-Inheritance in Haskell can be achieved through class extension, which involves a class defined as a subclass 
-of another class. The subclass then inherits all of the operations in the superclass. A benefit to class 
+Inheritance in Haskell can be achieved through class extension, which involves defining a class as a subclass 
+of some other class. The subclass then inherits all of the operations in the superclass. A benefit to class 
 extension is shorter contexts: a type expression for a function that uses operations from both the subclass 
@@
 
-The following class definition of Ord inherits all of the operations in Eq, but also includes the comparison 
-operators as well as maximum and minimum functions.
+The following class definition of the \texttt{Ord} typeclass inherits all of the operations in the \texttt{Eq} typeclass but
+also obtains comparison operators as well as the \texttt{maximum} and \texttt{minimum} functions.
 

### 2013-04-22 projects/term_paper/paper.tex
Finished the exception handling section.

@@
 
+Haskell, like many other languages, provides ways to utilize error handling code
+in the event of abnormal program execution.  However, Haskell is
+different from other languages in the sense that the preferred way to handle
+these circumstances depends upon the portion of the code which requires action.
+To explain this point, functions in Haskell must be classifed as either pure
+or impure.  Recall the in previous sections, the Haskell language core was
+claimed to be pure functional programming in the sense the functions do
+not produce any side-effects beyond their output values.  However, certain
+functions in Haskell must break this trend in some respect; such functions include
+those responsible for I/O, concurrency, and interfaces to other languages~\cite{haskell-awkward-squad}.
+As a side note, this split from the functional paradigm for these types of functions has
+been mended by the introduction of monads in Haskell, a topic which unfortunately will not be covered here.
+
+For impure functions, \texttt{exceptions} are the favored way to perform error handling.
+The following example provides an error handling function \texttt{handler} associated with the
+\texttt{tryThis} function for intervening with I/O file-related issues.
+\begin{minted}{haskell}
+import System.Environment  
+import System.IO  
+import System.IO.Error
+
+main = tryThis `catch` handler
+
+tryThis :: IO ()  
+tryThis = do (fileName:_) <- getArgs  
+    fileContents <- readFile fileName  
+    putStrLn $ "File contains " 
+        ++ show (length (lines fileContents)) ++ " lines"
+
+handler :: IOError -> IO ()  
+handler e 
+    -- handle exception
+    | isDoesNotExistError e = putStrLn "The file does not exist."  
+    -- re-raise exception
+    | otherwise = ioError e  
+\end{minted}
+
+For pure functions, the Haskell typeclass system was broaded to allow the introduction
+of the \texttt{Maybe} algebraic type.  This type extension provides a function a way to
+indiciate that it may or may not return a value of the specified type in its declaration
+(i.e., it may fail to return any value).  If a function implementing this typeclass
+fails this way, the return value will be \texttt{Nothing}.  If it does return a value, say \texttt{x},
+that value will be prefaced by the keyword \texttt{Just}.  A pure function illustrating this concept
+is given below.
+\begin{minted}{haskell}
+doubleHead :: [Int] -> Maybe Int
+doubleHead [] = Nothing
+doubleHead xs = Just ((head xs) * 2)
+
+main = do
+    print (doubleHead [2,4,6])  -- output: Just 4
+    print (doubleHead [])       -- output: Nothing
+\end{minted}
+
 \section{Advanced Topics}

### 2013-04-22 projects/term_paper/paper.tex
Finished the paper and added a few more bibliography entries.

@@
 \begin{minted}{haskell}
+myExp :: (Num a) => a -> a
 myExp =
@@
 \subsubsection{Iterative Constructs}
-\bi
-    \item List comprehensions
+
+In Haskell, multiple constructs are supplied for the programmer to perform repetitive tasks including
+list comprehensions, map- and fold-style functions, and function recursion.
+
+List comprehensions in Haskell are a means to transform the elements in a list in some manner.
+To facilitate the transformation, multiple parts are in the construct are used: the input elements, the
+predicates, and the output function.  The iput elements are typically derived from another list.  Then,
+the predicates are applied to each of these elements in other to restrict the input set.  Finally, the
+restricted set then has the output function applied to every element in this set and the resuling list
+is returned.  An exmaple below is given where \texttt{xs} is the input list, \texttt{x `mod` 3 == 0} is
+a predicate used for filtering, and \texttt{x} is the simple output function.
 \begin{minted}{haskell}
@@
 \end{minted}
-    \item Map/fold
+
+Maps and folds are in many ways similar to list comprehensions.  In a map, a function is specified to apply to
+every element of a list to produce a new list.  A fold in Haskell aggregates all of the elements in a list into
+a single data type using some user-specified function.  An example using both map and reduce is given below.
+In this example, every element in a list is first squared (mapped) and the resulting list is then summed up (folded).
 \begin{minted}{haskell}
@@
 \end{minted}
-    \item Recursion
+
+All of the previous iterative constructs covered to this point share one thing in common:
+they all could be implemented by recursion.  Recursion is the fundamental construct for iterating
+in Haskell.  Recursion is implemented in functions in Haskell through pattern matching.  The boundary
+case in a recursive definition terminates the iteration; the recursive process is typically defined using pattern matching,
+where the boundary case is specificed with some pattern while the recurive case is set up as the default case.
+The function below demonstrates this scenario by pattern matching on an integer value of the input parameter \texttt{x}.
 \begin{minted}{haskell}
@@
 \end{minted}
-\ei
+
+It is worth noting that in Haskell, tail and guarded recursion are both utilized for improved performance 
+by minimizing the function frame allocations on the stack.  However, because of the lazy-evaluation philosophy of Haskell,
+recursions may be foregone until required, thereby negating the need for recursion optimization in some instances~\cite{haskell-tail-recur}.
 
 \subsubsection{Functions}
+
+Up to this point, several functions have been defined and used in the examples.  As Haskell is a functional programming
+language, functions are the primary modular construct employed to accomplish tasks.  Worth noting here, the parameter passing techniques
+supported in functions are by default explicit.  That is, bindings can be scoped to functions by explicitly invoking a function
+with the arguments that want to be scoped to the function in general.  However, there are a few notable exceptions that the community
+has developed to support implicit parameter passing to functions of some degree:
 \bi
-    \item Definition/use
-    \item Parameter passing techniques
+    \item Constant function definitions can be employed at the top level of a module~\cite{haskell-implicit-params}
+    \item Monads can be utilized to effectively hide global definitions~\cite{haskell-implicit-params}
 \ei
@@
 \subsubsection{Scoping}
-In Haskell, static scoping is employed.  As such, bindings are localized
-to the function in which they were defined or passed.
+In Haskell, static scoping is employed in resolving the origins of bindings.  As such, active bindings are first those localized
+to the function followed by global scope.  As such, bindings within callee functions are not active in the caller function
+unless explicitly passed as parameters.  This tenent of staticly binding within functions
+works toward the end of keeping functions from producing any side-effects~\cite{haskell-scope}.
 
 \subsubsection{Modules}
+
+Modules in Haskell are the basic unit of organizing functions and other constructs.  The standard Haskell library
+is composed of thousands of well-developed and maintained modules for a variety of purposes.  In the example below,
+three functions are defined and made available to any other program that imports this module.
+
 \begin{minted}{haskell}
@@
 
+In Haskell, there is a mature library of modules for built-in and extension-level
+concurrency and parallelism~\cite{haskell-concurr}.  Platforms supported for concurrent and parallel execution include shared- and
+distributed-memory systems, accelerator-style devices (e.g., general-purpose programming), and
+symmetric and unsymmetric architectures~\cite{par-funk}.  Multi-threading and multiprocessing capabilities are available in
+the standard Haskell library.  In the following example, multiple user-level threads are created for printing
+to the main terminal device, one of which prints the word ``Hello'' while the other prints ``world.''
+
+on graphics processing units)
+\begin{minted}{haskell}
+import Control.Concurrent
+import System.IO
+
+main :: IO ()
+main = do { forkIO (hPutStr stdout "Hello")
+            ; hPutStr stdout " world\n" }
+\end{minted}
+
 \subsection{Introspection and Reflection}

### 2013-04-22 projects/term_paper/paper.tex
Made edits to paper

@@
 This paper provides an overview of the Haskell programming language.  The sections are outlined as follows:
-section 1 describes the background surrounding Haskell, including its connections to functional programming,
+Section 1 describes the background surrounding Haskell, including its connections to functional programming
 and its usage today.  Section 2 provides a survey of many of the data and control constructs native to Haskell.
@@
 symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
-of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
-Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of 
-modern industry~\cite{haskell-wiki}.
+of computing.
 
@@
 its scope. This concept is referred to as having no ``side-effects,'' and this affords Haskell a certain simplicity in design
-and implementation, as well as lends itself to other means such as optimization toward parallel processing. In addition,
+and implementation, as well as lends it to other means such as optimization toward parallel processing. In addition,
 functions do not have to be declared in a particular order since they all exist independently of one another.
@@
 
-Haskell is most commonly used for the development of substantial software systems. The language is designed to produce
+Haskell is most commonly used for the development of substantial software systems. The language is designed to increase
 productivity from programmers in fewer lines of code. In addition, having no side-effects leads to fewer errors.
@@
 a compiled language, with the Glasgow Haskell Compiler (GHC) being the most common implementation,
-most of the type checking is done and enforced at compile time.
+most of the type checking is performed and enforced at compile time.
 
@@
 reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous, ordered collections of
-similar data types. Tuples, on the other hand, heterogeneous collections. Tuples are most useful when the types and exact number of 
+similar data types. Tuples, on the other hand, are heterogeneous collections. Tuples are most useful when the types and exact number of 
 values to be combined are known. Like lists, there is a wide array of built-in functions for tuples including, for instance,
@@
 string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. 
-It also helps increase the readability of code. In the following example, the data is stored in the representation of 
-str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in \texttt{str2}, 
+It also helps increase the readability of code.
+In the following example, \texttt{str1} shows how the data for a string is actually stored: as a list of characters.
+However, Haskell allows the definition of a string using double quotes, as seen in \texttt{str2},
 which is much more understandable.
@@
 do not meet the defined function type is flagged by the compiler, and compilation will be aborted. In addition, 
-use type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
+Haskell uses type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
 following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type 
@@
 read as ``has a type of.''  The types of the parameters can be listed in order, and the last type in the list 
-is the return type. The following function is called \texttt{greet}.
-
-It takes in a string and returns a string. The string is passed in as the variable \texttt{name}. Everything that follows 
-the equal sign is the expression, and the evaluation of this expression is the return value.
+is the return type.
+The following function is called \texttt{greet}.
+It takes in a string and returns a string.
+The string is passed in as the variable \texttt{name}.
+Everything that follows the equal sign is the expression, and the evaluation of this expression is the return value.
 
@@
 variables that are expressions themselves and are locally bound.  \texttt{let} bindings are often used for pattern matching. 
-The syntax of \texttt{let} bindings involved declaring the bindings inside a \texttt{let} declaration, followed by defining an 
+The syntax of \texttt{let} bindings involves declaring the bindings inside a \texttt{let} declaration, followed by defining an 
 expression inside an \texttt{in} declaration. The \texttt{let} and \texttt{in} statements must be aligned in the same column.
@@
 Operators in Haskell are typically represented with symbols. Some of the basic operators in Haskell include addition, 
-subtraction, multiplication, divison, exponentiation, concatenation, and equality operators and logic operators. The 
+subtraction, multiplication, divison, exponentiation, concatenation, and equality and logic operators. The 
 precedence of operators conform to the standard orders used in mathematics: exponentiation is highest, followed by 
-muliplication and visision, with addition and subtraction with the lowest precedence.
+muliplication and division, with addition and subtraction assuming the lowest precedence.
 
@@
 If-else statements in Haskell conform to the traditional syntax of the if-else selection construct. The only notable 
-difference is that Haskell requires that every conditional is followed by a then expression and an else expression. 
-The compiler will prevent compilation for any if conditional that does not also have then and else statements because 
+difference is that Haskell requires that every \texttt{if} conditional statement is followed by a \texttt{then} expression and an \texttt{else} expression. 
+The compiler will prevent compilation for any \texttt{if} conditional that does not also have \texttt{then} and \texttt{else} statements because 
 without them it would be possible for an input to cause a function not to have a return value, which Haskell does not allow.
@@
 If the condition is false, then the next guard condition is evaluated, and this pattern continues until the 
-`otherwise' guard is reached, which catches all input that did not match any guard previous conditions. The 
+\texttt{otherwise} guard is reached, which catches all input that did not match any guard previous conditions. The 
 following function has three guards, each following a pipe. A notable aspect of this function is that if the 
@@
 first guard expression even though the input would also be true for the second guard. This is because the guards are 
-checked in order, so the second guard is never checked because the first guard is true and the return value is 
-determined from it. The otherwise guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
+checked in the order which they are defined, so the second guard is never checked in this case because the first guard is true and the return value is 
+determined from it. The \texttt{otherwise} guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
 
@@
 starting with the first and proceeding accordingly.  If no match is made, an exception is raised.
-A default match can be speficied by listing `plain' variables as function parameters.
+A default match can be specified by using variables as function parameters rather than a pattern.
 
@@
 To facilitate the transformation, multiple parts are in the construct are used: the input elements, the
-predicates, and the output function.  The iput elements are typically derived from another list.  Then,
+predicates, and the output function.  The input elements are typically derived from another list.  Then,
 the predicates are applied to each of these elements in other to restrict the input set.  Finally, the
-restricted set then has the output function applied to every element in this set and the resuling list
-is returned.  An exmaple below is given where \texttt{xs} is the input list, \texttt{x `mod` 3 == 0} is
+restricted set then has the output function applied to every element in this set and the resulting list
+is returned.  An example below is given where \texttt{xs} is the input list, \texttt{x `mod` 3 == 0} is
 a predicate used for filtering, and \texttt{x} is the simple output function.
+
 \begin{minted}{haskell}
@@
 In this example, every element in a list is first squared (mapped) and the resulting list is then summed up (folded).
+
 \begin{minted}{haskell}
@@
 case in a recursive definition terminates the iteration; the recursive process is typically defined using pattern matching,
-where the boundary case is specificed with some pattern while the recurive case is set up as the default case.
+where the boundary case is specified with a pattern while the recursive case is set up as the default case.
 The function below demonstrates this scenario by pattern matching on an integer value of the input parameter \texttt{x}.
+
 \begin{minted}{haskell}
@@
 language, functions are the primary modular construct employed to accomplish tasks. Worth noting here, the parameter passing techniques
-supported in functions are by default explicit.  That is, bindings can be scoped to functions by explicitly invoking a function
+supported in functions are explicit by default. That is, bindings can be scoped to functions by explicitly invoking a function
 with the arguments that want to be scoped to the function in general. However, there are a few notable exceptions that the community
@@
 In Haskell, static scoping is employed in resolving the origins of bindings.  As such, active bindings are first those localized
-to the function followed by global scope.  As such, bindings within callee functions are not active in the caller function
+to the function followed by global scope.  Thus, bindings within callee functions are not active in the caller function
 unless explicitly passed as parameters.  This tenent of staticly binding within functions
@@
 To explain this point, functions in Haskell must be classifed as either pure
-or impure.  Recall the in previous sections, the Haskell language core was
-claimed to be pure functional programming in the sense the functions do
+or impure.  Recall that in previous sections, the Haskell language core was
+claimed to be a pure functional programming in the sense that functions do
 not produce any side-effects beyond their output values.  However, certain
@@
 \texttt{tryThis} function for intervening with I/O file-related issues.
+
 \begin{minted}{haskell}
@@
 
-For pure functions, the Haskell typeclass system was broaded to allow the introduction
+For pure functions, the Haskell typeclass system was broadened to allow the introduction
 of the \texttt{Maybe} algebraic type.  This type extension provides a function a way to
-indiciate that it may or may not return a value of the specified type in its declaration
+indicate that it may or may not return a value of the specified type in its declaration
 (i.e., it may fail to return any value).  If a function implementing this typeclass
@@
 In Haskell, there is a mature library of modules for built-in and extension-level
-concurrency and parallelism~\cite{haskell-concurr}.  Platforms supported for concurrent and parallel execution include shared- and
+concurrency and parallelism~\cite{haskell-concurr}.  Platforms that support concurrent and parallel execution include shared- and
 distributed-memory systems, accelerator-style devices (e.g., general-purpose programming), and

### 2013-04-22 projects/term_paper/paper.tex
More edits.

@@
 \usepackage{minted}
+\usepackage{url}
 
@@
 Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. The logo of Haskell, lambda,
-symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
+symbolizes that lambda calculus is the foundation from which Haskell was based. Today, Haskell is widely used in many different aspects 
 of computing.
@@
 
+Beside function independence, Haskell also follows the lazy function evaluation paradigm which characterizes some other functional 
+languages. Because of lazy evalution, functions in Haskell are not evaluated until their return value is needed by some other function.
+This leads to some interesting constructs that cannot be implemented in non-lazy languages, such as infinite lists.
+
 \subsection{Application Domains}
@@
 Haskell is most commonly used for the development of substantial software systems. The language is designed to increase
-productivity from programmers in fewer lines of code. In addition, having no side-effects leads to fewer errors.
-These features are very important in the development of large software systems, and Haskell is an ideal choice.
+productivity from programmers in fewer lines of code. In addition, fewer errors are often produced by developers due to the lack of
+side-effects in functions.  These features are very important in the development of large software systems, and Haskell is an ideal choice.
 
@@
 Haskell supports a very rich, strong, static type system for programmers.  As Haskell is
-a compiled language, with the Glasgow Haskell Compiler (GHC) being the most common implementation,
+a compiled language --- with the Glasgow Haskell Compiler (GHC) being the most common implementation ---
 most of the type checking is performed and enforced at compile time.
@@
 
-Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
+Haskell also allows definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
 are not their own data type. Although string literals can be initialized using the double quote syntax, the compiler converts the 
@@
 In addition to these basic data types, Haskell also offers type variables. Type variables are variables whose type has 
-not been explicitly declared; rather, they can be any type.  By defining a function without declaring data types, the 
+not been explicitly declared; rather, they can be any type.  Type variables are most often employed to define the parameter
+and return value types of functions. By defining a function without declaring data types, the 
 variables in the function can be used as any type thereby enabling polymorphic behaviors. In the following example, the 
@@
 do not meet the defined function type is flagged by the compiler, and compilation will be aborted. In addition, 
-Haskell uses type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
-following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type 
-is desired because myNum is added to an Int.
+Haskell supports type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
+following example, the \texttt{read} function is used to convert \texttt{myStr} to another data type.
+Although the type of \texttt{myNum} is unknown at compile time, the compiler infers that the Int type 
+is desired because \texttt{myStr} is added to an Int type.
 
@@
 let myStr = "2" 
-let myNum2 = (read myStr) + 2
+let myNum = (read myStr) + 2
 \end{minted}
@@
 
+To avoid ambiguity in type conversion, the following syntax can be employed to indicated to the compiler what type
+is desired from the \texttt{read} function.
+
+\begin{minted}{haskell}
+let myStr = "2"
+let myNum = (read myStr) :: Float
+\end{minted}
+
 Haskell uses typeclasses to categorize the type system. Typeclasses define the behavior of a general type. 
@@
 Show, Read, Enum, Num, Integral, and Floating. Typeclasses can be used to allow multiple types to be passed to a 
-function. In the following example, the function declares its typeclass as Integral. Therefore, the function will 
-allow accept Int or Integer types as parameters.
+function. In the following example, the function declares its typeclass as Integral. Therefore, valid functions invocations consist
+of Int or Integer type parameters.
 
@@
 \subsection{Control Abstractions}
-\subsubsection{Expressions}
+
+Haskell supports several constructs for controlling program execution.  These constructs can be further divided into:
+expressions, functions, and operators, selection and iteration mechanisms, modules, and execption handling.
+In order to further understand the functionality of these constructs, scoping and parameter passing techniques are discussed.
+
+\subsubsection{Expressions and Functions}
 
@@
 The syntax of \texttt{let} bindings involves declaring the bindings inside a \texttt{let} declaration, followed by defining an 
-expression inside an \texttt{in} declaration. The \texttt{let} and \texttt{in} statements must be aligned in the same column.
+expression inside an \texttt{in} declaration. The expression in the \texttt{let} and \texttt{in} parts must be aligned in the same column.
 
@@
 myExp :: (Num a) => a -> a
-myExp =
+myExp x =
     let e = 2.7182
@@
 The difference between \texttt{let} and \texttt{where} bindings is that \texttt{let} bindings are expressions themselves, whereas 
-\texttt{where} bindings are just syntactic constructs. Additionally, unlike \texttt{where} bindings, \texttt{let} bindings cannot 
-span across guards.
+\texttt{where} bindings are just syntactic constructs attached to some expresion. 
+Additionally, unlike \texttt{where} bindings, \texttt{let} bindings cannot span across guards.
 
@@
 
-If-else statements are not used in Haskell as often as they are in imperative languages because Haskell offers a feature 
+If-else statements are not used in Haskell as often as they are in imperative languages because Haskell offers another feature 
 known as guards, which are fundamentally equivalent to if-else statements except they are much more easily understood, 
@@
 first guard expression even though the input would also be true for the second guard. This is because the guards are 
-checked in the order which they are defined, so the second guard is never checked in this case because the first guard is true and the return value is 
-determined from it. The \texttt{otherwise} guard is placed at the bottom to catch any value that does not cause the first two guards to be true.
+checked in the order which they are defined, so the second guard is never checked in this case because the first guard is true and 
+the return value is  determined from it. The \texttt{otherwise} guard is placed at the bottom to catch any value that does not 
+cause the first two guards to be true.
 
+\newpage
 \begin{minted}{haskell}
@@
 
-\subsubsection{Functions}
+\subsubsection{Functions and Parameter Passing}
 
@@
 is given below.
+\newpage
 \begin{minted}{haskell}

### 2013-04-22 projects/term_paper/src/InfixPostfix.hs

@@ -41,7 +41,8 @@ infixToPostfix expr =
         removeToLeftParen (x:xs) = removeToLeftParen xs
 
         parseExpr [] stack = 
-            (foldl (++) "" (zipWith (++) stack (replicate (length stack - 1) " ")))
+            (foldl (++) "" (zipWith (++) 
+                stack (replicate (length stack - 1) " ")))
             ++ (last stack)
         parseExpr (x:xs) stack
             | isOperand x = x ++ " " ++ (parseExpr xs stack)
